\tool: Revisiting BadUSB with Type-C

### 2021-01-30 WOOT/Files/experiment.tex
fix a typo

\begin{table*}[t]
	\centering
	\begin{tabular}{|l|l|l|l|}
		\hline
		\textbf{Keyword} & \textbf{Text}                                                             & \textbf{Name}                                   & \textbackslash{}textbf\{Frame Number\} \\ \hline
		username                          & X 8B cas.******.edu.cn Username: 11****18 Password:                                        & \textless{}user1\textgreater{} & 385                                    \\ \hline
		username                          & Login Weibo Login with SMS and verification code ...... +86 151****4587                    & \textless{}user5\textgreater{} & 1947                                   \\ \hline
		username                          & QQ 14*****50| Login with phone number New user registration 2345678 9 0                    & \textless{}user3\textgreater{} & 4308                                   \\ \hline
		username                          & connect to *** username h*****l Save account information Open VPN.....                     & \textless{}user6\textgreater{} & 7925                                   \\ \hline
		phone number                      & Login with phone number ...... +86 186****2483 |                                           & \textless{}user1\textgreater{} & 313                                    \\ \hline
		phone number                      & Log in with your mobile phone number. ...... mobile phone number 131****9310 & \textless{}user9\textgreater{} & 210                                    \\ \hline
		@                                 & contact email 30*******7G@qq.com, contact phone 027-88******                               & \textless{}user7\textgreater{} & 5324                                   \\ \hline
		@                                 & Account 73*****5@qq.com @qq.com @163.com @gmail.com 	......      & \textless{}user6\textgreater{} & 621                                    \\ \hline
	\end{tabular}
	\linebreak
	\caption{Examples of Searching OCR Results with Keywords.}
	\label{tab:ocr_keyword_example}
\end{table*}

>>>>

\begin{table*}[t]
	\centering
	\begin{tabular}{|l|l|l|l|}
		\hline
		\textbf{Keyword} & \textbf{Text}                                                             & \textbf{Name}                                   & \textbf{Frame Number} \\ \hline
		username                          & X 8B cas.******.edu.cn Username: 11****18 Password:                                        & \textless{}user1\textgreater{} & 385                                    \\ \hline
		username                          & Login Weibo Login with SMS and verification code ...... +86 151****4587                    & \textless{}user5\textgreater{} & 1947                                   \\ \hline
		username                          & QQ 14*****50| Login with phone number New user registration 2345678 9 0                    & \textless{}user3\textgreater{} & 4308                                   \\ \hline
		username                          & connect to *** username h*****l Save account information Open VPN.....                     & \textless{}user6\textgreater{} & 7925                                   \\ \hline
		phone number                      & Login with phone number ...... +86 186****2483 |                                           & \textless{}user1\textgreater{} & 313                                    \\ \hline
		phone number                      & Log in with your mobile phone number. ...... mobile phone number 131****9310 & \textless{}user9\textgreater{} & 210                                    \\ \hline
		@                                 & contact email 30*******7G@qq.com, contact phone 027-88******                               & \textless{}user7\textgreater{} & 5324                                   \\ \hline
		@                                 & Account 73*****5@qq.com @qq.com @163.com @gmail.com 	......      & \textless{}user6\textgreater{} & 621                                    \\ \hline
	\end{tabular}
	\linebreak
	\caption{Examples of Searching OCR Results with Keywords.}
	\label{tab:ocr_keyword_example}
\end{table*}
